An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-30 VLDB2026/main.tex
chang 4.2.2

	Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building. ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing. In database systems (VBASE, PASE, Milvus), when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree. Hence, they are excluded from this comparison.

@@

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.  CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) UNG has poor performance because large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. The performance of CAPS is as good as that of Puck. The difference between them is that CAPS further groups the results by attributes within clusters. In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

>>>>

	Faiss offers an ID filtering mechanism, it operates solely during query execution and does not influence index building. ACORN-1 and ACORN-\(\gamma\) are specifically designed for single-attribute indexing. In database systems (VBASE, PASE, Milvus), \sout{when the system builds both B+ tree and vector indexes, queries typically utilize only the B+ tree.} 
	\textcolor{red}{The attributes do not participate in index construction.}
	Hence, they are excluded from this comparison.

@@

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.  CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) UNG has poor performance because large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, \sout{degenerating into a situation closer to inverted retrieval,} and the effect may be greatly impaired.

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. The performance of CAPS is as good as that of Puck. \sout{The difference between them is that CAPS further groups the results by attributes within clusters.} In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.
